---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 5,
  fig.height = 4
)
library(bisonpicsuite)
```

# bisonpicsuite

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/bisonpicsuite/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/bisonpicsuite/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/bisonpicsuite/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/bisonpicsuite)
<!-- badges: end -->

The goal of `bisonpicsuite` is to make it easy to install and load the `bisonpic` suite of
R packages for visualizing and analyzing wood **BISON** camera trap (**PIC**) data.

The packages are designed to facilitate data exploration and analysis of wood bison camera trap data, using underlying functions to visualize and analyze data (`bisonpictools`) and Shiny applications that streamline the data visualization (`shinybisonpic`) and data analysis (`runbisonpic`) processes.

The data are analyzed using an Bayesian Integrated Population Model, which combines a stage-structured population projection matrix model with multiple sources of data into a unified framework, allowing for estimates of age-sex class ratios, population vital rates, and abundances, while maintaining the correct propagation of uncertainty.
See the [analytical methods](https://poissonconsulting.github.io/bisonpictools/articles/bisonpic-methods.html) vignette for more detail on the modeling approach.

## Installation

You can install the latest version of `bisonpicsuite` from [GitHub](https://github.com/poissonconsulting/bisonpicsuite) with:

``` {r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/bisonpicsuite")
```

## Load

To load `bisonpicsuite`, execute the following line of code.

```{r}
library(bisonpicsuite)
```

### Packages

The packages installed and loaded by `bisonpicsuite` suite are:

- [bisonpictools](https://github.com/poissonconsulting/bisonpictools)
- [shinybisonpic](https://github.com/poissonconsulting/shinybisonpic)
- [runbisonpic](https://github.com/poissonconsulting/runbisonpic)

## Inspiration

`bisonpicsuite` was inspired by the [`tidyverse`](https://github.com/tidyverse/tidyverse) package.

## Information

Additional information is available from the [`bisonpicsuite`](https://poissonconsulting.github.io/bisonpicsuite/) and [`bisonpictools`](https://poissonconsulting.github.io/bisonpictools/) websites, which contain the following articles:

- `bisonpicsuite`
  - [Getting Started with bisonpicsuite](https://poissonconsulting.github.io/bisonpicsuite/articles/bisonpicsuite-getting-started.html)
  - [Bisonpic User Guide](https://poissonconsulting.github.io/bisonpicsuite/articles/bisonpic-user-guide.html)

- `bisonpictools`
  - [Getting Started with bisonpictools](https://poissonconsulting.github.io/bisonpictools/articles/bisonpictools-getting-started.html)
  - [Analytical Methods](https://poissonconsulting.github.io/bisonpictools/articles/bisonpic-methods.html)

## Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/poissonconsulting/bisonpicsuite/issues/).

## How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](https://github.com/poissonconsulting/bisonpicsuite/blob/master/.github/CONTRIBUTING.md) guidelines.

## Code of Conduct

Please note that the `bisonpicsuite` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

```{r, results = "asis", echo = FALSE}
cat(bisonpictools::bpt_licensing_md())
```
